Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-10-01 eqm_profiles.tex
add state variable details and dependence of each players' strategies on it
add period 1 strategies

\vskip.3in

>>>>

\vskip.3in
First, need to get timing clear for evolution of state variable. Take state variable to be $q_{st}$.
\begin{itemize}
	\item $q_{s1}$: beginning of the world (or, $Q_{s0} - \mu = q_{s1}$)
	\item $Q_{s1} = q_{s1} + R_{p1} + R_{c1}$
		\begin{itemize}
			\item $q_{s2} = Q_{s1} - \mu$
		\end{itemize}
\end{itemize}

Strategies
\begin{itemize}
	\item For patron: function of $q_{st}$
	\item For c: function of $q_{st} + R_{pt}$
	\item For s: function of $Q_{st}=q_{st} + R_{pt} + R_{ct}$
	\item For g: not a function of $q_{st}$ at all
\end{itemize}

For Markov-perfect equilibrium, strategy profile must be dependent on state variable, $q_{s}$ only.

\vskip.5in
Period 1
\begin{itemize}
	\item Patron: $R_{p1} = \frac{\beta}{1-\de} - \left(q_{s1} - l_{s1}\right)$ to augment $q_{s1}$ if this is greater than 0. Else, $R_{p1} = 0$. Can write in max language.
	\item International community: If $R_{p1} + q_{s1} - l_{s1} \geq \frac{\beta}{1-\de}$, $R_{c1} =0$. Otherwise $R_{c1} = l_{s1} - \left(q_{s1} + R_{p1} \right)$ to augment $l_{s1}$.
	\item Gov't / Secessionists: Choose unilateral, simultaneous best responses depending on magnitudes of $Q_{i1}$, $L_{i1}$ and $\omega{i1}$
\end{itemize}
